{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2015-10-29 paper.tex
A few corrections.

Let $\mbox{H}$ denote the constant Hessian of the cost function:
$$
\mbox{H} = \left(\begin{array}{cccccc}
(\lambda_{0}+\lambda_{1})\weight^2 & -\lambda_{1}\weight^2 & 0 & \cdots & & 0 \\
-\lambda_{1}\weight^2 & (\lambda_{1}+\lambda_{2})\weight^2 & -\lambda_{2}\weight^2 & 0 & \cdots & 0 \\
0 & -\lambda_{2}\weight^2 &  (\lambda_{2}+\lambda_{3})\weight^2 & -\lambda_{3}\weight^2 & 0 & \vdots \\
\vdots & \ddots & \ddots & \ddots & \ddots & \vdots\\
\vdots & & \ddots & \ddots & \ddots & \vdots\\
0 & \cdots  & 0 & -\lambda_{wp-2}\weight^2 & (\lambda_{wp-2}+\lambda_{wp-1})\weight^2 & -\lambda_{wp-1}\weight^2 \\
0 & \cdots &  \cdots & 0 & -\lambda_{wp-1}\weight^2 & (\lambda_{wp-1}+\lambda_{wp})\weight^2  \\
\end{array}\right)
$$

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be a 
contact point expressed in the global frame 
(Figure~\ref{contact-points} left). We compute the respective positions $\po_1$ and 
$\po_2$ of $\po_c$ in 
the local frames of $\body_1$ and $\body_2$ (Figure~\ref{contact-points} right).

@@

Notice that $\mathbf{u}$ is well defined since configuration 
$\xx_{i}(t_{coll\ i})$ is collision-free.
Let $g$ be the function defined from $\CS$ to $\real$ by:
$$
g (\conf) = \left(M_{1}^{-1} (\conf) M_2 (\conf) \po_2 - \po_1 | \mathbf{u}\right)
$$
where $\po_1$ and $\po_2$ are computed in the configuration $\conf$. The function $g$ 
represents the projection of $\overrightarrow{\po_1\po_2}$ on $\mathbf{u}$ which is calculated 
from the last collision-free path at abscissa $\tcolli$.

@@

Thus the velocity of point $\po_2$ in the reference frame of $\body_1$ projected onto $\mathbf{u}$ along the motion of the robot is given by:
$$
\frac{\partial \conf}{\partial t}(t) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_i + t\alpha_i\xx_{i+1})\p_i
$$
Therefore the following expressions
% \frac{\partial \conf}{\partial t}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \text{and} \ \frac{\partial \conf}{\partial t}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
\dot{\conf}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \ \text{and} \ \ \dot{\conf}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
correspond to $\dot{\po_2}(\xx).\mathbf{u}$, respectively in configurations $\xx_{i}(t_{coll\ i})$ and $\xx_{i+1}(t_{coll\ i})$. The term $\dot{\conf}(1)$ being equal to zero requires either:
\begin {enumerate}
\item that $\po_1$ and $\po_2$ come to contact at zero velocity, or
\item the velocity of $\po_2$ in the reference frame of $\body_1$ is orthogonal to 
$\mathbf{u}$ at contact ($t=1$).
\end {enumerate}
The first case is very unlikely and almost never encountered in real applications, 
except if the user builds such a case on purpose.
The second case may appear and can be noted by a rank loss of $\Jf_{i+1}$.
Then we do not directly insert the new constraint. Instead, we process intermediate 
iterations until the redundancy vanishes, as explained in function 
\texttt{findNewConstraint} and illustrated in (Figure~\ref{fig:convergence-diagram}).

@@

\begin{figure}
	\centering
	\includegraphics[width=15.8cm]{convergence-diagram.pdf}
	\caption{Representation of the trajectory $\conf (t)$ from 
	Equation~(\ref{eq:trajectory}) in the 
	configuration space (left). For the same trajectory in the workspace, the 
	colliding bodies are illustrated. Note that a case with 
	$\dot{\po_2}(\xx_{Free}).\mathbf{u}=0$ is considered. Therefore, 
	(Algorithm~\ref{algo:solveRedundant}) will produce one intermediate step
	$\xx$ (gray path and clear bodies). $\xx$ is collision-free and 
	$\dot{\po_2}(\xx).\mathbf{u}\neq 0$ so the redundancy is solved and the
	constraint will be linearized on $\xx$.}
	\label{fig:convergence-diagram}
\end{figure}

@@

In this section, the GB path-optimizer (Algorithm~\ref{algo:gradient}) is described
according to the previous steps definitions. One difficulty here is to handle 
the scalar parameter $\alpha$ determining how much of the computed step $\p$ will 
be traveled through. Typically, we 
chose $\alpha_{init} = 0.2$ or 0.1 to process small steps. $\alpha_{init} = 0.5$ is 
more encountered in the optimization literature, procuring larger steps but with 
more risks of collision.

>>>>

From the gradient expression, we notice that the Hessian $\mbox{H}$ is constant:
$$
\mbox{H} = \left(\begin{array}{cccccc}
(\lambda_{0}+\lambda_{1})\weight^2 & -\lambda_{1}\weight^2 & 0 & \cdots & & 0 \\
-\lambda_{1}\weight^2 & (\lambda_{1}+\lambda_{2})\weight^2 & -\lambda_{2}\weight^2 & 0 & \cdots & 0 \\
0 & -\lambda_{2}\weight^2 &  (\lambda_{2}+\lambda_{3})\weight^2 & -\lambda_{3}\weight^2 & 0 & \vdots \\
\vdots & \ddots & \ddots & \ddots & \ddots & \vdots\\
\vdots & & \ddots & \ddots & \ddots & \vdots\\
0 & \cdots  & 0 & -\lambda_{wp-2}\weight^2 & (\lambda_{wp-2}+\lambda_{wp-1})\weight^2 & -\lambda_{wp-1}\weight^2 \\
0 & \cdots &  \cdots & 0 & -\lambda_{wp-1}\weight^2 & (\lambda_{wp-1}+\lambda_{wp})\weight^2  \\
\end{array}\right)
$$

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be a 
contact point expressed in the global frame 
(Figure~\ref{contact-points} left). We define $\po_1$ and $\po_2$ as the coordinates of $\po_c$ in the  respective local frames of $\body_1$ and $\body_2$ (Figure~\ref{contact-points} right).

@@

Notice that $\mathbf{u}$ is well defined since configuration 
$\xx_{i}(t_{coll\ i})$ is collision-free.
Let $g$ be the function defined from $\CS$ to $\real$ by:
$$
g (\conf) = \left(M_{1}^{-1} (\conf) M_2 (\conf) \po_2 - \po_1 | \mathbf{u}\right)
$$
The function $g$
represents the projection of $\overrightarrow{\po_1\po_2}$ on $\mathbf{u}$ which is calculated 
from the last collision-free path at abscissa $\tcolli$.

@@

Thus the velocity of point $\po_2$ in the reference frame of $\body_1$ projected onto $\mathbf{u}$ along the motion of the robot is given by:
$$
 \dot{\conf}(t) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_i + t\alpha_i\xx_{i+1})\p_i
$$
Therefore the following expressions
% \frac{\partial \conf}{\partial t}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \text{and} \ \frac{\partial \conf}{\partial t}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
\dot{\conf}(0) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i})\p_i \ \ \text{and} \ \ \dot{\conf}(1) = \alpha_i \frac{\partial f}{\partial \xx}(\xx_{i+1})\p_i
$$
correspond to $\dot{\po_2}(\xx).\mathbf{u}$, respectively in configurations $\xx_{i}(t_{coll\ i})$ and $\xx_{i+1}(t_{coll\ i})$. The term $\dot{\conf}(1)$ being equal to zero requires either:
\begin {enumerate}
\item that $\po_1$ and $\po_2$ come to contact at zero velocity, or
\item the velocity of $\po_2$ in the reference frame of $\body_1$ is orthogonal to 
$\mathbf{u}$ at contact ($t=1$).
\end {enumerate}
The first case is very unlikely and almost never encountered in real applications, 
except if the user builds such a case on purpose.
The second case may appear and can be noted by a rank loss of $\Jf_{i+1}$.
Then we do not directly insert the new constraint. Instead, we process intermediate 
iterations until the redundancy vanishes, as explained in function 
\texttt{findNewConstraint} and illustrated in (Figure~\ref{fig:convergence-diagram}).

@@

\begin{figure}
	\centering
	\includegraphics[width=15.8cm]{convergence-diagram.pdf}
	\caption{Representation of the trajectory $\conf (t)$ from 
	Equation~(\ref{eq:trajectory}) in the 
	configuration space (left). For the same trajectory in the workspace, the 
	colliding bodies are illustrated. Note that a case with 
	$\dot{\po_2}(\xx_{Free}).\mathbf{u}=0$ is considered. Therefore, 
	(Algorithm~\ref{algo:solveRedundant}) will produce one intermediate step
	$\xx$ (gray path and clear bodies). $\xx$ is collision-free and 
	$\dot{\po_2}(\xx).\mathbf{u}\neq 0$ so the redundancy is solved and the
	constraint will be linearized around $\xx$.}
	\label{fig:convergence-diagram}
\end{figure}

@@

In this section, the GB path-optimizer (Algorithm~\ref{algo:gradient}) is described
according to the previous steps definitions. One difficulty here is to handle 
the scalar parameter $\alpha$ determining how much of the computed step $\p$ will 
be traveled through. Typically, we 
chose $\alpha_{init} = 0.2$ or 0.1 to process small steps.
